Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-17 manuscript/manuscript.Rmd

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.

>>>>

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
There are a variety of fixed points for the equations---around 7 or 8 for wide ranges of parameter values.
Fig. \ref{fig:tbd} provides a rough idea of the fixed point structure by plotting the bifurcation diagram obtained from varying $D$ and fixing the other parameters.

Throughout most of this paper we will fix the parameters of the model according to Table \ref{tab:tbd}.
At these values, the fixed points of the model are:
\begin{align*}
  TBD
\end{align*}
The classification of fixed points for multi-dimensional systems is generally more complicated than in one dimension.
A fixed point might be stable against perturbations in one direction, but unstable against perturbations along another.
While a detailed classification of these fixed points is beyond the scope of this work, we point out that the point $(TBD)$ is stable against perturbations in all directions.
We will thus use it as a starting point for our simulations.
